%%
%% Resume template updated 05/25/2018
%% Notes: occasional manual page breaks are necessary, \vspace{-2.5mm} for
%% all bullets except the first
%% TODO: change tenses on Boston things to make them in the past

\documentclass{article}
\usepackage{anysize}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{nopageno}
\marginsize{1.5cm}{1.5cm}{.3cm}{1cm}

\newcommand{\s}[1]{\vspace{4mm} \noindent \large \textbf{#1} \\[-2.5mm] \linethickness{0.2mm} \line(1,0){515}}
\newcommand{\n}{\\ \noindent \normalsize}
\newcommand{\nl}{\noindent \normalsize}
% Use nl instead of n in some places

\begin{document}
\begin{center}
	\huge \textbf{Ayman Ali} \\
	\vspace{2.0mm} \small Contact - ayman.ali1230@gmail.com
\end{center}

\s{Education}
	\n \textbf{Tulane University School of Medicine, Doctor of Medicine} \hfill M.D. Class of 2022
	\n \textbf{University of Connecticut, Bachelor of Science, Mathematics}  \hfill August 2012 - May 2016
	% \n \textit{Bachelor of Science, Mathematics} \\
	% \indent Dean's List \hfill Fall 2014 - Spring 2016 \\
	% \indent New England Scholar \hfill 2015  \\
%	\n \textbf{Coursework \& Research Concentrations}
%	\vspace{-3.5mm}
%		\begin{multicols}{3} 
%			\begin{itemize} [noitemsep]
%            	\item Probability 
%            	\item Statistics
%            	\item Computational Physics
%            	\item Real \& Complex Analysis 
%            	\item Thermodynamics
%            	\item Stochastic Modeling
%            	\item Medical Decision Science
%				\item Health Outcomes Research
%				\item Stroke
%				\item Neonatal Encephalopathy
%				\item Esophageal and Thyroid Cancer
%				\item Pulmonary Embolism
%        	\end{itemize}
%    	\end{multicols}
%    	\vspace{-3.5mm}
   \n \textbf{Programming}
        \begin{itemize}
			%\vspace{-2.5mm} \item Spoken: English, Urdu, and Hindi.
			%\vspace{-2.5mm} \item Programming: Fluency in C++ and Python. Proficiency in C. Familiarity with R and SQL.
		\vspace{-2.5 mm} \item Fluency in C\texttt{++}, Python, and C. Familiar with R and SQL.
		\vspace{-2.5 mm} \item Experience using the Boost library, TensorFlow, Python standard libraries, and scikit-learn.
	  \end{itemize}
	    \vspace{-3.5mm}
	        		    	
\s{Publications}

	\begin{enumerate}
		\item \nl \textbf{Ali A}, Nudel J, Heberle CR, Santorino D, Olson KR, Hur C. ``Cost Effectiveness of a Novel Device for Imrpoving Resuscitation of Apneic Newborns". BMC Pediatrics. BMC Pediatrics. 2020 Jan 30. 

		\item \nl Omidvari AH, \textbf{Ali A}, Hazelton WD, Kroep S, Lee M, Naber SK, Lauren BN, Ostvar S, Richmond E, Kong CY, Rubenstein JH, Lansdorp-Vogelaar I, Luebeck G, Hur C, Inadomi J. ``Optimizing Management of Patients With Barrett's Esophagus and Low-grade or No Dysplasia Based On Comparative Modeling: Optimizing Barrett's Esophagus Management." Clin Gastroenterol Hepatol. 2019 Dec 6. 

		\item \nl Choi JG, Nipp RD, Tramontano A, \textbf{Ali A}, Zhan T, Pandharipande P, Dowling EC, Ferrone CR, Hong TS, Schrag D, Fernandez-Del Castillo C, Ryan DP, Kong CY, Hur C. ``Neoadjuvant FOLFIRINOX for Patients with Borderline Resectable or Locally Advanced Pancreatic Cancer: Results of a Decision Analysis." Oncologist. 2018 Dec 17.

		\item \nl White C, Weinstein MC, Fingeret AL, Randolph GW, Miyauchi A, Ito Y, Zhan T, \textbf{Ali A}, Gazelle GS, Lubitz CC. ``Is Less More? A Microsimulation Model Comparing Cost-effectiveness of the Revised American Thyroid Association's 2015 to 2009 Guidelines for the Management of Patients With Thyroid Nodules and Differentiated Thyroid Cancer." Ann Surg. 2018 October 17.

		\item \nl \textbf{Ali A}*, Zachrison KS*, Eschenfeldt PC, Schwamm LH, Hur C. ``Optimization of Prehospital Triage of Patients with Suspected Ischemic Stroke: Results of a Mathematical Model''. Stroke. 2018 Oct. *Co-first authors.

		\item \nl \textbf{Ali A}*, Zhan T*, Choi JG, Lee M, Leung J, Dellon ES, Garber JJ, Hur C. ``Model to Determine the Optimal Dietary Elimination Strategy for Treatment of Eosinophilic Esophagitis''. Clin Gastroenterol Hepatol. 2018 Nov. *Co-first authors.
		
		\item \nl Kabrhel C, \textbf{Ali A}, Choi JG, Hur C. ``Systemic Thrombolysis, Catheter-Directed Thrombolysis, and Anticoagulation for Intermediate-Risk Pulmonary Embolism: A Simulation Modeling Analysis''. Acad Emerg Med. 2017 Oct.
		
		\item Lubitz C, \textbf{Ali A}, Zhan T, Heberle CR, White C, Gazelle GS, Kong CY, Hur C. ``The Thyroid Cancer Policy Model: A Mathematical Simulation Model of Papillary Thyroid Carcinoma in The U.S. Population''. PLOS One. 2017 May 8.		
		
		\item Heberle C, Omidvari A, \textbf{Ali A}, Kreop S, Inadomi JM, Rubenstein JH, Tramontano AC, Dowling DC, Hazelton WD, Luebeck EG, Lansdorp-Vogelaar I, Hur C.  ``Cost-Effectiveness of Screening Patients with Gastroesophageal Reflux Disease for Barrett's Esophagus With a Minimally Invasive Cell Sampling Device.'' Clin Gastroenterol Hepatol. 2017 Sep.
		
		\item Kroep S, Heberle CR, Curtius K, Kong CY, Landsdorp-Vogelaar I, \textbf{Ali A},  Wolf WA, Shaheen NJ, Spechler SJ, Rubenstein JH, Nishioka NS, Meltzer SJ, Hazelton WD, van Ballegooijen M, Tramontano AC, Gazelle GS, Luebeck EG, Inadomi JM, Hur C. ``Radiofrequency Ablation of Barrett's Esophagus Reduces Esophageal Adenocarcinoma Incidence and Mortality in a Comparative Modeling Analysis." Clin Gastroenterol Hepatol. 2017 Sep.
		
	\end{enumerate}

	\vspace{-2.5mm}

\s{Abstracts, Posters, and Presentations}
	
	\begin{enumerate}

		\item \nl Vahdatzad V, \textbf{Ali A}, Digennaro C, Toumi A, Jalali M, Hur C, Chhatwal J, Lubitz C. "A Micro-simulation Model for the Natural History of Progression of Benign and Malignant Thyroid Nodules: Comparison of Calibration Methods". [Poster, ISPOR - The Professional Society for Health Economics and Outcomes Research, Orlando Fl, May 2020] [Did not present]

		\item \nl \textbf{Ali A}, Friedman J, Tatum D, Jones G, Guidry C, McGrew P, Schroll R, Harris C, Duchesne J, Taghavi S. “Does Payer Status Influence Injury Pattern in Pediatric Bicycle Injuries?”. [QuickShot Presentation, Academic Surgical Congress, Orlando Fl, February 2020]

		\item \nl \textbf{Ali A}, Tatum D, Jones G, Guidry C, McGrew P, Schroll R, Harris C, Duchesne J, Taghavi S. “Pediatric Pelvic Fracture Outcomes in Pediatric versus Adult Trauma Centers?”. [QuickShot Presentation, Academic Surgical Congress, Orlando Fl, February 2020]

		\item \nl Zachrison KS, Truong HQ, Eschenfeldt PC, Ingram MA, \textbf{Ali A}, Hur C, Schwamm LH. ``Optimal Prehospital Stroke Triage is Highly Dependent on Individual Hospital Reperfusion Times". [Poster, International Stroke Conference, Los Angeles LA, February 2020] [Did not present]

		\item \nl \textbf{Ali A}, Friedman J, Tatum D, Jones G, Guidry C, McGrew P, Schroll R, Harris C, Duchesne J, Taghavi S. “Does Payer Status Influence Injury Pattern in Pediatric Bicycle Injuries?”. [Poster, Louisiana Chapter Academic Surgical Congress, New Orleans LA, January 2020]

		\item \nl \textbf{Ali A}, Tatum D, Jones G, Guidry C, McGrew P, Schroll R, Harris C, Duchesne J, Taghavi S. “Pediatric Pelvic Fracture Outcomes in Pediatric versus Adult Trauma Centers?”. [Poster, Louisiana Chapter Academic Surgical Congress, New Orleans LA, January 2020]

		\item \nl \textbf{Ali A}, Eschenfeldt P, Zachrison K, Schwamm L, Hur C. ``Modeling Pre-hospital Triage Decisions for Patients with Suspected Stroke Due to Severe Large Vessel Occlusion''. [Speaker, The NorthEast Cerebrovascular Consortium, Newport RI, October 2017]. \textbf{Recipient of \$10,000 funding award} as the winner of ``Stroke Tank: Pitch It to the Judges!''.
	
		\item \nl Choi JG, Nipp RD, Tramontano A, \textbf{Ali A}, Zhan T, Kong CY, Pandharipande P, Dowling E, Ferrone C, Hong TS, Schrag D, Castillo CF, Ryan DP, Hur C. ``Neoadjuvant FOLFIRINOX for patients with borderline resectable or locally advanced pancreatic cancer: Results of a decision analysis". [Poster, American Society of Clinical Oncology, Chicago IL, June 2017] [Did not present]
		
		\item Zhan T*, \textbf{Ali A}*,  Choi JG, Kim D, Garber J, Hur C. ``Optimal Food Elimination Strategy for Eosinophilic Esophagitis''. [Poster, Digestive Disease Week, Chicago IL, May 2017]. *Co-First Authors [Did not present]
	
		\item \textbf{Ali A}, Kabrhel C, Choi J, Hur C. ``Catheter-Directed Thrombolysis for Intermediate-Risk Pulmonary Embolism: A Simulation Modeling Analysis''. [Poster, Society of Academic Emergency Medicine Annual Meeting 2017,  Orlando FL, May 2017].
	
		\item Choi JG, \textbf{Ali A}, Hur C, Lubitz SA. ``Population Screening for Atrial Fibrillation: Results of a Cost-Effectiveness Modeling Analysis''. [Poster, Heart Rhythm 2017, Chicago IL, May 2017] [Did not present]
	
		\item \textbf{Ali A}, Heberle C, Omidvari A, Kreop S, Inadomi JM, Rubenstein JH, Tramontano AC, Dowling DC, Hazelton WD, Luebeck EG, Lansdorp-Vogelaar I, Hur C.  ``Cost-Effectiveness of Screening Patients with Gastroesophageal Reflux Disease for Barrett's Esophagus With a Minimally Invasive Cell Sampling Device.'' [Poster, Hampton Symposium, The Massachusetts General Hospital Radiological Society / Harvard Medical School, March 2017].
		
		\item Zhan T, \textbf{Ali A}, Heberle CR, White C, Gazelle GS, Kong CY, Hur C, Lubitz C. ``The Thyroid Cancer Policy Model: A Mathematical Simulation Model of Papillary Thyroid Carcinoma in The U.S. Population''. [Poster, Hampton Symposium, The Massachusetts General Hospital Radiological Society / Harvard Medical School, March 2017].
		
		\item \textbf{Ali A}, Kabrhel C, Choi J, Hur C. ``Catheter-Directed Thrombolysis for Intermediate-Risk Pulmonary Embolism: A Simulation Modeling Analysis''.  [Presentation, New England Research Director's Society for Academic Emergency Medicine, Worcester MA, March 2017].
	
	\end{enumerate}

	\vspace{-3.5mm}	

\s{Employment History}
	\vspace{2.0mm}
	\nl \textbf{Institute for Technology Assessment, Massachusetts General Hospital} \hfill Boston, Massachusetts
	\n \textit{Programmer Analyst and Researcher} \hfill June 2016 - August 2018
	\begin{itemize}
		\item Created and developed mathematical models (C/C\texttt{++}) of esophageal and thyroid cancer. 
		\vspace{-2.5mm} \item Built medical decision models (C/C\texttt{++}/Python) of various diseases such as pulmonary embolism, stroke, eosinophilic esophagitis, and neonatal encephalopathy.
	\end{itemize}

	\nl \textbf{Cambridge Biomedical and Economic Consulting Group LLC} \hfill Boston, Massachusetts
	\n \textit{Analyst} \hfill August 2017 - June 2018
	\begin{itemize}
		\item Lead project analyst for development of health-economic models. 
		\vspace{-2.5mm} \item Clients included large pharmaceutical companies in the Greater Boston region. 
	\end{itemize}

	\nl \textbf{Hazmat Response Team, Massachusetts General Hospital} \hfill Boston, Massachusetts
	\n \textit{Volunteer} \hfill October 2016 - June 2018
	\begin{itemize}
		\item Emergency response volunteer, on call every third month.
		\vspace{-2.5mm} \item Trained in preparation for a variety of circumstances, such as extreme weather and specific chemical, biological, radiological, or nuclear threats.
	\end{itemize}

	\nl \textbf{Psychology Department, University of Connecticut} \hfill Storrs, Connecticut
	\n \textit{Research Assistant} \hfill August 2015 - May 2016
	\begin{itemize}
		\item Coded for experiments (simulations, virtual reality, and games) using Unity and C\#. 
		\vspace{-2.5mm} \item Supervised participants and running experiments. 	
		\vspace{-2.5mm} \item Aided in experimental design. 	
	\end{itemize}
	
	\nl \textbf{Quantitative Learning Center, University of Connecticut} \hfill Storrs, Connecticut
	\n \textit{Mathematics, Physics, and Statistics Tutor} \hfill August 2014 - May 2016
	\begin{itemize}
		\item Tutored students with a focus on developing, strengthening, and applying analytical skills to quantitative problems.
		\vspace{-2.5mm} \item Specific subjects included all introductory calculus, physics, and statistics classes, probability, differential equations, multivariable calculus, and linear algebra. 
	\end{itemize}			
	
	\nl \textbf{Prime Healthcare of Southport} \hfill Fairfield, Connecticut
	\n \textit{Medical Receptionist} \hfill May 2014 - May 2016
	\begin{itemize}
		\item Organized and handled incoming patient information such as prescription refills, consultation reports, and bloodwork.
		\vspace{-2.5mm} \item Worked with various insurance and pharmaceutical companies in order to get patients coverage for medically necessary procedures, treatments, and drugs (most commonly through prior authorizations).
		\vspace{-2.5mm} \item Scheduled patients and checked them in, in addition to submitting and following up on insurance claims. 
		\vspace{-2.5mm} \item  Wrote and completed clinical notes.
	\end{itemize}

	\vspace{-3.5mm}	

\s{Community \& Service}
	\vspace{2.0mm}
	\nl \textbf{Science Fair Mentor, Massachusetts General Hospital} \hfill Boston, Massachusetts
	\n \textit{Volunteer} \hfill September 2016 - May 2018
		\begin{itemize}
			\item Worked with children from city public middle schools with their science fair projects, serving as a guide and tutor. 
			\vspace{-2.5mm} \item Taught components of research in STEM with an underlying understanding that most students did not have access to computers. 
		\end{itemize}
		
	\nl \textbf{Kids and UConn Bridging Education} \hfill Storrs, Connecticut
	\n \textit{Volunteer} \hfill August 2015 - May 2016
		\begin{itemize}
			\item Mentored children from low-income neighborhoods around the University of Connecticut with the goal to build literacy, social involvement, and aspiration.
		\end {itemize}
		
	\nl \textbf{Global Scholars Project} \hfill Pakistan
		\n \textit{Field Worker} \hfill Spring 2013
			\begin{itemize}
				\item Traveled to isolated areas of Pakistan to provide impoverished children with means to a proper education.
				\vspace{-2.5mm} \item Enhanced and strengthened education programs by providing schools (founded on previous trips) with computers containing pre-installed information, in order to circumvent lack of internet and frequency of load shedding.
				\vspace{-2.5mm} \item In charge of documentation of the trip, including administering interviews with students and teachers in order to potentially improve the effectiveness and long-term sustainability of the programs.
			\end {itemize}
			
	
	\nl \textbf{Red Cross Society at the University of Connecticut} \hfill Storrs, Connecticut
	\n \textit{Awareness Chair} \hfill September 2012 - September 2014
		\begin{itemize}
			\item Built and maintained a strong network of volunteers at the university from student organizations. 
			\vspace{-2.5mm} \item Oversaw and supervised drives for a minimum of 20 hours a semester, serving as the primary contact for questions by volunteers, donors, or red cross officials. 
			\vspace{-2.5mm} \item Created presentations and workshops to train and educate students interesting in volunteering at drives. 
		\end{itemize}

	\vspace{-3.5mm}	

\s{Personal}
	\vspace{2.0mm}
	\nl \textbf{Grappling, Wrestling, and Brazilian Jiu Jitsu} \hfill 2016 - Present
		\begin{itemize}
			\item Approximately 10 - 15 hours per week of training throughout medical school.
			\vspace{-2.5mm} \item Occasional teaching and competition involvement. 
			\vspace{-2.5mm} \item Competition: December 1st, 2018 -- 2nd place, beginner division
			\vspace{-2.5mm} \item Competition December 7st, 2019 -- 2nd place, intermediate / advanced division
		\end{itemize}
\end{document}